### 2019-02-10 paper.tex
Wip

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item Project maintainers use \emph{Guild files}---simple YAML files
  included with project source---to document and automate project
  capabilities such as supported models, operations, hyperparameter
  defaults and search space for optimization experiments.

@@

\textbf{Command Line Interface, Visualization, API.} Guild's primary
user interface is a command line interface, which integrates
efficiently with other system tools. Guild additionally provides a
graphical, web based dashboard to explore and analyze runs and
integration with TensorBoard. Guild also exposes functionality in a
Python API for application developers.

\textbf{Cross Framework and Language Support.} Guild supports any
learning script that generates experiment results. Models may be
implemented in any language, framework, or software library.

@@

Guild facilitates reproducibility by automating experiments,
systematically capturing results, and providing tools for analysis and
comparison. A typical workflow in Guild is:

\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt]
\item Run trials for a baseline model
\item Run trials for novel work
\item Compare and analyze results
\item Optionally package and distribute project code to further
  simplify reproducibility
\end{enumerate}

@@

Automation tools in machine learning commonly require tool-specific
changes to project source code. This generally includes adoption of a
Python API for controlling experiments, accessing hyperparameters and
logging results. Automation tools may also require additional system
software such as databases, container management systems, and job
schedulers.

Each requirement that a tool imposes on a user presents a barrier to
the goal of systematic machine learning. In some cases, researchers
may view the cost of automation in support reproducibility to
outweight the benefit.

To encourage systematic machine learning, Guild does not require
changes to user code or installation and maintenance of external
systems. Users run their training scripts without modification. For
example, an unmodified Python script \texttt{train.py} that supports
hyperparameters \texttt{n\_layers} and \texttt{lr} may be run using a
command such as:

@@

Guild supports this workflow without external dependencies.

Guild additionally supports easy packaging, distribution, and
installation of research work in the support of reproducibility. To
our knowledge, no other tool provides this feature.

@@

We propose an interactive demonstration that highlights the benefits
of fast, easy experiment reproduction. Throughout the session, the
presenter refers to two personas---represented visually with
placards---to help viewers maintain context for various scenario:

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Influence}. Work that is easier to reproduce is more
  likely to influence others, other factors held constant.

@@

\textbf{Scenarios}. The demonstration is structured flexibly to
encourage questions, input, and redirection from the audience. While
presented below as a natural sequence, scenarios are presented and
discussed in any order according to audience expectation and interest.

@@

\item \emph{Clegane} conducts a survey of related work, reproducing
  published results where possible. He clones Arya's repository and
  uses Guild to reproduce her findings. He further experiments with
  changes to Arya's model and hyperparameters to build a stronger
  intuition for his summary.

\item \emph{Clegane} contacts Arya to discuss her work and answer
  questions he has based on his own experiments. He uses Guild to
  publish trials to S3 where Arya can access them.

\item \emph{Arya} pulls Clegane's results from S3 and uses Guild to
  study the differences between her results and Clegane's and uses
  this information to answer his questions.

@@

The presenter supplies a laptop with HDMI and brings supporting
graphical placards and other visual aids to reference during
scenarios. To avoid problems with network connectivity, the
demonstration is disconnected from the network. Demonstrations of
networking features (e.g. copying experiment results to and from S3)
are run locally over a proxy, but are nonetheless live and unmocked.

>>>>

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item Project maintainers use \emph{Guild files}---simple YAML files
  included with project source---to document and automate project
  capabilities such as supported models, operations, hyperparameter
  defaults and optimization search space.

@@

\textbf{Command Line Interface, Visualization, API.} Guild's primary
user interface is a command line interface, which integrates
efficiently with other system tools. Guild additionally provides a
graphical, web based dashboard to explore and analyze runs and
integration with TensorBoard. Guild also exposes functionality in a
Python API for advanced scripting and application developers, though
this interface is not required for general use.

\textbf{Cross Framework and Language Support.} Guild supports any
learning script that generates experiment results. Models may be
implemented in any framework or library including but not limited to
TensorFlow, PyTorch, scikit-learn, Keras, MXNet, or language such as
Python, R, Go, and Java.

@@

Guild supports reproducibility by automating experiments, capturing
results, and providing tools for analysis, comparison, and sharing. A
typical workflow in Guild is:

\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt]
\item Run trials for a baseline model
\item Run trials for novel work
\item Compare and analyze results
\item Optionally package and distribute project work to further
  simplify reproducibility
\end{enumerate}

@@

Automation tools in machine learning commonly require tool-specific
changes to project source code. This generally includes adoption of a
Python API for controlling experiments, accessing hyperparameters and
logging results. Automation tools may further require additional
system software such as databases, container management systems, and
job schedulers.

Each requirement that a tool imposes on a user presents a barrier to
the goal of systematic machine learning. In some cases, researchers
and engineers may view the cost of supporting reproducibility to
outweigh the benefits.

To encourage systematic machine learning, Guild runs unmodified
learning scripts without requiring the installation and maintenance of
external systems. Once Guild is installed, for example, an unmodified
Python script \texttt{train.py} that supports hyperparameters
\texttt{n\_layers} and \texttt{lr} can be run using:

@@

Guild additionally supports easy packaging, distribution, and
installation of research work in the support of machine learning
reproducibility. To our knowledge, no other tool provides this
feature.

@@

We propose an interactive demonstration that highlights the benefits
of fast, easy experiment reproduction. Throughout the session, the
presenter refers to two personas---represented visually with
placards---to help viewers maintain context during various scenario:

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Influence}. Work that is easier to reproduce is more
  likely to influence others, other factors being equal.

@@

\textbf{Scenarios}. The demonstration is structured flexibly to
encourage questions, input, and redirection from the audience. While
presented below as a sequence, scenarios are presented and discussed
in any order according to audience interest.

@@

\item \emph{Clegane} conducts a survey of related work, reproducing
  published results where possible. He clones Arya's repository and
  uses Guild to reproduce her findings. He further experiments with
  changes to Arya's model and hyperparameters to develop a deeper
  understanding for his summary.

\item \emph{Clegane} contacts Arya to discuss her work and present
  questions he has based on his own experiments. He uses Guild to
  publish hist results to S3 where Arya can access them.

\item \emph{Arya} pulls Clegane's results from S3 and uses Guild to
  study the differences between her results and his. She uses this
  information to answer Clegane's questions.

@@

The presenter supplies a laptop with an HDMI interface and brings
supporting graphical placards and other visual aids to reference
during scenarios. To avoid problems with network connectivity, the
demonstration is disconnected from the network. Demonstrations of
networking features (e.g. copying experiment results to and from S3)
are run locally over a proxy, but are nonetheless live and unmocked.
